Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-02 02_Paper/paper.tex
update structure
extra sections.

\section{Introduction} % 1 Page (incl authors, abstract)

@@

\section{Related Works} % 1 Page

\subsection{Quality check in production} % Basic books (find summarize) basic concepts

% a)	How quality check is done in production
%        i)	Concepts and sampling plan
%        ii)	Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]

@@

% b)	Predictive analytics in production focusing in QA
%        i)	Existing approaches and methods

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page

% What is the demozelle and why it is relevant as study case
% a)	Description of the assemble process in the Demozelle 
% Incl pictures

\section{Methods} %3/4 Page

% b)	Data  is collected from the demonstration cell and analyzed 
% c)	ML model [regression] is trained [type of model tbd]

\section{Experiments} % 1.5 Pages

\subsection{Lesson Learned} % 1/2 Page

@@

\section{Conclusion} % 1/2 Page

>>>>

\section{Introduction}

@@

\section{Related Works}

\subsection{Quality check in production}

% b)	How quality check is done in production
%        i)	Concepts and sampling plan
%        ii)	Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]

@@

% a)	Predictive analytics in production focusing in QA
%        i)	Existing approaches and methods

\section{The Demo-Cell}

% What is the demozelle and why it is relevant as study case

\section{Methods}

% a)	Description of the assemble process in the Demozelle 
% b)	Data  is collected from the demonstration cell and analyzed 
% c)	ML model [regression] is trained [type of model tbd]
\subsection{Measurement}

\subsection{Machine Learning}

\section{Experiments}

\subsection{Recording the data}

\subsection{Classifier optimization and testing}

\begin{table}
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100\%
       \end{tabular}
       \caption{Method comparison for fault detection using the industry demo data test set.}
\end{table}

\section{Conclusion}

\subsection{Lesson Learned}

@@
